---
title: "Surpassing the R vs Python dogma"
author: "Dana Jomar, Clemens Zauchner"
date: "May 2019"
output: 
  ioslides_presentation:
    toc: true
    df_print: null
    theme: null
    css: style.css
    widescreen: true
    keep_md: true
    #smaller: true  ## only works without "---" slide breaks (use ##)
    slide_level: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      eval = TRUE,
                      results = 'asis')
```

## Contents

- Background?
- Feather
- Ursa / Apache Arrow
- Rstudio 1.2 / reticulated python

## Why?

- A lot of data science teams use both
- both languages have rich interfaces to C++
- most of under-the-hood coding is done in C++

## Feather

## Ursa Labs

## Apache Arrow

## Rstudio 1.2 / reticulated python

- A package that makes it possible to embed a Python session within an R process.
- Provides wrapper functions to use python modules and scripts
  + import, python_source, repl_python, use_python, py_install, …… 
- Data conversion back and forth between the two languages happens through C++.
- R and Python variables are accessible from both environments.
  + The objects  py and r provide this access.
  
## Type conversion

```{r}
r <- c('Single-element vector','Multi-element vector','List of multiple types',
       'Named list','Matrix/Array','Data Frame','Function','NULL, TRUE, FALSE')

py <- c('Scalar','List','Tuple','Dict','NumPy ndarray','Pandas DataFrame',
        'Python function','None, True, False')

ex <- c('1, 1L, TRUE, "foo"','c(1.0, 2.0, 3.0), c(1L, 2L, 3L)','list(1L, TRUE, "foo")',
        'list(a = 1L, b = 2.0), dict(x = x_data)','matrix(c(1,2,3,4), nrow = 2, ncol = 2)',
        'data.frame(x = c(1,2,3), y = c("a", "b", "c"))','function(x) x + 1','NULL, TRUE, FALSE')

source <- 'https://rstudio.github.io/reticulate/'
  
  

library(tableHTML)

data.frame(R = r,
           Python = py,
           Examples = ex) %>% 
  tableHTML(rownames = FALSE,
            widths = c(200, 200, 300),
            footer = paste0("source: ", source)) %>% 
  tableHTML_to_image(zoom = 2)

```


## test

```{r}
grid::grid.raster(png::readPNG('python-logo-master-v3-TM.png'))
```


